Approximating the Optimal State Abstraction

### 2015-10-07 state_abstraction.tex
updated post meeting

% Subsection: Things you should not compress on.
\subsection{Result 3: Collapsing on just {\it state variables}, or {\it reward}, or {\it other?} is insufficient to preserve any kind of optimality (including $\epsilon$-optimality.}

@@

% --- SECTION: New Proposal ---
\newpage
\section{New Proposal: Approximate Abstraction}

For each of the following three cases:
% Model Equivalence
\begin{equation}
 \phi(s_1) = \phi(s_2) \rightarrow \forall_{s,a} : T(s \mid s_i, a) = T(s \mid s_j, a)
\end{equation}

@@

% Optimal action and value Equivalence
\begin{equation}
 \phi(s_1) = \phi(s_2) \rightarrow \argmax_a Q^*(s_i, a) = \argmax_a Q^*(s_j, a) \wedge \max_a Q^*(s_i, a) = \max_a Q^*(s_j, a)
\end{equation}

Relax the equality condition, instead consider the approximate case, e.g.:
% Model Similarity
\begin{equation}
 \phi(s_1) = \phi(s_2) \rightarrow \forall_{s,a} : |T(s \mid s_i, a) - T(s \mid s_j, a)| \leq \epsilon
\end{equation}

\elem{The Question:} Can anything be said about the optimality of the policy $\pi_{\phi_{T,\epsilon}}$ in the ground MDP? Are we within some factor of $\epsilon$ away from being optimal?

% --- SECTION: Temporal Abstraction ---
\newpage
\section{New Proposal: Temporal Abstraction}

@@

>>>>

@@

% --- SECTION: New Proposal ---
\newpage
\section{New Proposal 1: Approximate Abstraction}

For each of the following four cases:

% Model Equivalence
\begin{equation}
 \phi(s_1) = \phi(s_2) \rightarrow \forall_{s,a} : T(s \mid s_1, a) = T(s \mid s_2, a) \wedge \forall_a : R(s_1,a) = R(s_2,a)
\end{equation}

% Transition Equivalence
\begin{equation}
 \phi(s_1) = \phi(s_2) \rightarrow \forall_{s,a} : T(s \mid s_i, a) = T(s \mid s_j, a)
\end{equation}

@@

% Optimal action and Q value Equivalence
\begin{equation}
 \phi(s_1) = \phi(s_2) \rightarrow \argmax_a Q^*(s_i, a) = \argmax_a Q^*(s_j, a) \wedge \max_a Q^*(s_i, a) = \max_a Q^*(s_j, a)
\end{equation}

% Possible I-Learning?

% Ordering of Q values?

\elem{Our strategy:} relax the equality condition, instead consider the approximate case, e.g.:
% Model Similarity
\begin{equation}
 \phi(s_1) = \phi(s_2) \rightarrow \forall_{s,a} : |T(s \mid s_i, a) - T(s \mid s_j, a)| \leq \epsilon
\end{equation}

\subsection{The Question:} Suppose we're given the optimal policy in the abstract MDP under one of the above approximate abstractions, e.g. $\pi^*_{\phi_{T,\epsilon}}$. What can be said about the potential optimality of this policy in the original ground MDP? (for each of the four approximate abstractions).

Note: Similar to simulation lemma from $E^3$, lets take a look.

% --- SECTION: Temporal Abstraction ---
\newpage
\section{New Proposal 2: Temporal Abstraction}

@@

% --- SECTION: Other Fruits ---
\newpage
\section{Other Low Hanging Fruit Results}

% Subsection: Things you should not compress on.
\subsection{Result 3: Collapsing on just {\it state variables}, or {\it reward}, or {\it value} is insufficient to preserve any kind of optimality (including $\epsilon$-optimality.}
